Interpolation and Extrapolation Performance Measurement of Analytical and ANN-Based Flow Laws for Hot Deformation Behavior of Medium Carbon Steel

### 2023-03-22 Article.tex
Remove highlights

%=================================================================
% MDPI internal commands - do not modify
% MDPI internal commands - do not modify
\firstpage{1}
\makeatletter
\setcounter{page}{\@firstpage}
\makeatother
\pubvolume{1}
\issuenum{1}
\articlenumber{0}
\pubyear{2023}
\copyrightyear{2023}
\externaleditor{Academic Editor: \hl{Ji Hoon Kim} %MDPI: Please add it.
}
\datereceived{ 10 February 2023}
\daterevised{ 16 March 2023} % Comment out if no revised date
\dateaccepted{20 March 2023}
\datepublished{ }
%\datecorrected{} % For corrected papers: "Corrected: XXX" date in the original paper.
%\dateretracted{} % For corrected papers: "Retracted: XXX" date in the original paper.
\hreflink{https://doi.org/} % If needed use \linebreak
%\doinum{}
%\pdfoutput=1 % Uncommented for upload to arXiv.org

@@

\DeclareRobustCommand{\w}{\mbox{\large\ensuremath{\mathsf{w}}}}
\DeclareRobustCommand{\dotp}{\boldsymbol{\cdot}}
\DeclareRobustCommand{\e}[1]{{\rm e}^{#1}}
\DeclareRobustCommand{\lay}[1]{^{(#1)}}
\DeclareRobustCommand{\mdot}[1]{\accentset{\mbox{\bfseries .}}{#1}}
\DeclareRobustCommand{\ie}{i.e.,\@\xspace}
\DeclareRobustCommand{\eal}{et al.\@\xspace}
\DeclareRobustCommand{\eg}{e.g.,\@\xspace}
\DeclareRobustCommand{\RMSE}{\text{E}_\text{RMS}}
\DeclareRobustCommand{\MARE}{\text{E}_\text{MAR}}
\DeclareRobustCommand{\R}{\text{R}}
\DeclareRobustCommand{\ps}{\text{s}^{-1}}
\DeclareRobustCommand{\mr}[2]{\multirow{#1}{*}{#2}}
\DeclareRobustCommand{\MPa}{\text{MPa}}
\newcommand{\hlok}[1]{\colorbox{green}{#1}}

@@

% Authors, for the paper (add full first names)
\Author{\hlok{Pierre Tize Mha} %Please carefully check the accuracy of names and affiliations. Changes will not be possible after proofreading. All names are correct
$^{1}$, Prashant Dhondapure $^{2}$, Mohammad Jahazi $^{2}$\orcidB{}, Amèvi Tongne $^{1}$\orcidC{} and Olivier Pantalé $^{1,}$*\orcidA{}}

@@

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{$^{1}$ \quad Laboratoire Génie de Production, INP/ENIT, Université de Toulouse, 47 Av d'Azereix, F-65016 Tarbes, France; \hlok{ptizemha@enit.fr (P.T.M.); amevi.tongne@enit.fr (A.T.)} %MDPI: We added emails from our system. Please confirm. OK
\\
$^{2}$ \quad Department of Mechanical Engineering, École de Technologie Supérieure, 1100 Notre Dame St. W., \hlok{Montréal,} %MDPI: We suggest to use English format city name. we add the department information, please confirm. OK
 QC H3C 1K3, Canada; prashant-nagnath.dhondapure.1@ens.etsmtl.ca (P.D.); mohammad.jahazi@etsmtl.ca (M.J.)}

@@

% Keywords
\keyword{\hlok{artificial} %mdpi: please check the first letter format (uppercase/lowercase) for every word in keywords. please check all the keywords. we suggest to use lowercase if the uppercase is not necessary: OK
neural network; constitutive flow law; analytical flow law; interpolation; extrapolation; Gleeble}

@@

\newcolumntype{L}{>{\raggedright\arraybackslash}X}
\newcolumntype{C}{>{\centering\arraybackslash}X}
\begin{tabularx}{\textwidth}{LCCCCCCC}
\toprule
\textbf{Element} & \textbf{C} & \textbf{Mn} & \textbf{Mo} & \textbf{Si} & \textbf{Ni} & \textbf{Cr} & \textbf{Cu} \\
\midrule
\textbf{\hlok{Wt}%MDPI: Is the bold necessary?. You can remove the bold, if it does not correspond to the editorial line of the journal.
~\%} & $0.30$ & $0.89$ & $0.52$ & $0.34$ & $0.68$ & $1.86$ & $0.17$ \\
\bottomrule
\end{tabularx}
\label{tab:Composition}
\end{table}
Cylindrical samples were machined with an initial diameter of $d=10$~mm and a height of $h_0=15$~mm.
Hot compression tests were performed on a Gleeble-3800 thermomechanical simulator (see Figure \ref{fig:Gleeble3800}), for $5$ temperature levels, namely $1050~\celsius$, $1100~\celsius$, $1150~\celsius$, $1200~\celsius$, and $1250~\celsius$, with the $6$ strain rates of $0.001~\ps$, $0.01~\ps$, $0.1~\ps$, $1~\ps$, $2.0~\ps$, and $5~\ps$.
\begin{figure}[H]

@@

\includegraphics[width=0.99\columnwidth]{Figures/CompExp-JC-6}
\caption{\hlok{Comparison} %MDPI: Many figures are very similar. Please confirm there is no duplicate figure. No, every figure is different, the name of the figure correspond to the section, and everything is OK.
 between the experimental (dots) and predicted (lines) flow stresses $\sigma^y$ by the Johnson--Cook model.}
\label{fig:CompExp-JC-6}
\end{figure}
The JC model is unable to describe the evolution of the average flow stress for all strain and strain rate levels. The experimental flow stresses show a growth and then a decrease with strain, especially for low strain rates, while the JC model, by its formulation, only allows an increasing evolution of the flow stress $\sigma^y$ as a function of the strain independently of the strain rate value.
The discrepancy between the predicted and experimental values is large for low strains and sometimes acceptable for high strains.
As expected, the mathematical formulation of the Johnson--Cook flow law is unable to represent the stress drop at low strain rates, with the JC model increasing only monotonically with the strain.
Since most of the parameters are identified at low strain rates ($A$, $B$, and $n$), this results in a very poor fit of the model to the experimental data.

@@

\includegraphics[width=0.7\columnwidth]
{Figures/ANN-scheme-2HL}
\caption{\hlok{Two} %MDPI: Should green and red dot be explained?. Caption modified.
 hidden layers artificial neural network architecture with 3 inputs neurons (green) and 1 output neuron (red).}
\label{fig:ANN-2HL}
\end{figure}

Any hidden layer $k$, containing $n$ neurons, takes a weighted sum of the outputs $\overrightarrow{\hat{y}}$ of the immediately preceding layer $(k-1)$, containing $m$ neurons, given by the following~equation:
\begin{equation}
y_i\lay{k} = \sum_{j=1}^m w_{ij}\lay{k} \hat{y}_j^{(k-1)}+ b_i\lay{k},\label{eq:ANN1}
\end{equation}
where $y_i\lay{k}$ is the entry of the  $i$th neuron of layer $k$, $\hat{y}_j\lay{k-1}$ is the output \hlok{of the} %MDPI: We suggest to remove the superscript and italic format of ``th''. Please check all the ``th''. Notation has been changed following your request.
  $j$th neuron of layer $(k-1)$, $w_{ij}\lay{k}$ is the associated weight parameter between the  $i$th neuron of layer $k$ and the  $j$th neuron of layer $(k-1)$, and $b_i\lay{k}$ is the associated bias of the  $i$th neuron of layer $k$.
Those weights $w_{ij}$ and bias $b_i$, for each layer, are the training parameters of the ANN, which we have to adjust during the training procedure described in Pantalé \eal \cite{Pantale-2021, Pantale-2023}.
For the proposed model, we selected the Sigmoid activation function, so that each neuron in the hidden layer $k$ provides an output value ${\hat{y}}$ from the input value $y$ of the same neuron defined by Equation (\ref{eq:ANN1}) according to the following equation:
\begin{equation}
\hat{y}=\frac{1}{1 + \e{-y}}\label{eq:ANN2}
\end{equation}

@@

\textls[-25]{Once the training phase is over, the trained model can be used to predict the behavior of the medium carbon alloy as a function of the input data, similarly to what was done with the analytical models.
One can either use the model directly by providing it with new input data or retrieve the $180$ parameters identified during the training and inject them into a mathematical model based on Equations (\ref{eq:ANN1}) and (\ref{eq:ANN2}), which can be implemented in any language (\eg in FORTRAN for use on the Abaqus Explicit FEA code), as proposed in Pantalé \eal \cite{Pantale-2021, Pantale-2023}.
For compactness, the parameters of the ANN model and the complete procedure to compute the flow stress $\sigma^y$ from the input data are provided in \hlok{Appendix} %MDPI: We changed Appendix to Appendix A. OK
 \ref{sec:Appendix}.}

@@

The ANN, Arrhenius and PTM models are the only models that take into account softening with the deformation of medium carbon at a low strain rate, unlike the other three models, which only present an increase in the flow stress with the strain, irrespective of the strain rate and temperature, hence their poor performance in predicting the behavior of this material and, more particularly, at low strain rates.
The parameters reported in \mbox{Table \ref{tab:Errors}} and the correlations that can be seen in Figures \ref{fig:CompExp-JC-6}\hlok{--}%MDPI: We changed ``to'' to en dash. OOPS, there is a mistake, it's figures 6,7,8,9,10, and 13. Figures 11 and 12 cannot be included in this list. I updated the cross references.
\ref{fig:CompExp-PTM-6} and \ref{fig:CompExp-3-15-7-1-sigmoid} allow concluding that the ANN model is the most efficient of all the models presented when it comes to describing the behavior of the medium carbon alloy for high-temperature deformation applications.

@@

\includegraphics[width=0.98\columnwidth]
{Figures/CompExt}
\caption{\hlok{Comparison} %MDPI: Should hyphen be changed to en dash in 3-15-7-1?. No, since, this will lead to longuer notations, I have used hyphen instead of en dash to reduce the width of the notation ANN-3-15-7-1-sigmoid for the model.
 between the experimental (dots) and predicted (lines) flow stresses $\sigma^y$ for $\mdot\varepsilon=5~\ps$.}
\label{fig:CompExt}
\end{figure}
Table \ref{tab:ExtVal} shows the $\MARE$ and $\RMSE$ deviations between the different models and the experimental data calculated either for the $5$ identified strain rates (lines referred as id. $\mdot\varepsilon$), the $6$ strain rates (lines referred as all $\mdot\varepsilon$), or only on the strain rate $\mdot\varepsilon=5~\ps$.
\begin{table}[H]

@@

\acknowledgments{The authors acknowledge \hlok{Jean}-Benoit Morin, \hlok{Director of} %MDPI: Titles should be removed in this part. Please revise
 Metallurgy and Quality from Finkl Steel-Sorel, \hlok{Abdelhalim} Loucif from the R\&D department of Finkl Steel-Sorel, Ecole de Technologie Superieure, and Ecole Nationale d'Ingenieurs de Tarbes, France, for providing technical data, materials, and testing facilities.}%MDPI: We removed titles here: OK

@@

\hlok{The} %MDPI: We added indent. OK
 biases of the first hidden layer $\overrightarrow{b_1}$ is a $15$-component vector:
\begin{equation*}
\overrightarrow{b}_1 = \left[
\begin{array}{r}
5.9164 \\
-1.9074 \\
-2.6837 \\
-1.0954 \\
-0.9509 \\
3.1682 \\
-4.3964 \\
0.6343 \\
-5.0676 \\
2.0228 \\
1.1267 \\
-0.9671 \\
-0.6263 \\
2.3110 \\
-0.3037
\end{array}\right]
\end{equation*}

\hlok{The} weight matrix for the second hidden layer $\w_2$ is a $7\times15$ matrix:
\begin{equation*}
\w_2^T = \left[
\begin{array}{rrrrrrr}
-0.5783 & 1.2724 & 0.5747 & 0.6449 & -4.2203 & -0.2380 & 0.2591 \\
-0.4852 & 5.2807 & 0.8888 & -8.2324 & -2.0075 & -0.6474 & -1.0787 \\
4.4499 & -0.0137 & 0.1657 & 0.3198 & 4.9765 & -1.2503 & 0.8219 \\
1.7571 & 0.7730 & 0.0208 & -1.3316 & -0.8945 & -0.7284 & -0.1831 \\
-1.0866 & 0.1330 & -0.8615 & -0.1283 & 0.2218 & -0.1772 & -2.7458 \\
-0.3925 & 1.3994 & 0.0630 & -1.8397 & -1.1047 & -1.9839 & 0.5767 \\
-0.2121 & 0.9977 & 1.2028 & -9.6525 & 0.5520 & 0.1062 & -0.0409 \\
-1.1518 & -1.6402 & -4.1501 & -1.0759 & 0.4749 & -2.8350 & 0.9225 \\
-1.1453 & -0.2173 & -0.1382 & 0.8264 & -0.5125 & 0.1882 & -0.8654 \\
-4.3301 & -0.3711 & -7.4305 & 3.5926 & -9.6217 & -1.2375 & 1.6171 \\
2.3907 & -1.0085 & -0.8828 & -1.1891 & 0.9947 & 1.1178 & -1.0953 \\
-1.5955 & 1.6313 & 0.4916 & 0.1906 & -1.9216 & -1.4140 & 1.3827 \\
-1.6985 & 1.4277 & -3.4462 & -8.3777 & -1.2132 & -1.2158 & 2.8512 \\
-1.9954 & -2.0159 & -8.3455 & -0.5205 & 0.2942 & -1.3337 & 0.2026 \\
4.3040 & -0.7164 & -1.0859 & 3.4294 & -23.8003 & 12.5859 & 7.3721
\end{array}\right]
\end{equation*}

\hlok{The} biases of the second hidden layer $\overrightarrow{b_2}$ is a seven-component vector:
\begin{equation*}
\overrightarrow{b}_2 = \left[
\begin{array}{r}
0.7534 \\
0.9473 \\
0.6055 \\
-0.7793 \\
-1.0305 \\
-1.5779 \\
-0.1471
\end{array}\right]
\end{equation*}

\hlok{The} weight vector for the output layer $\overrightarrow{w}$ is a seven-component vector:
\begin{equation*}
\overrightarrow{w} = \left[
\begin{array}{r}
0.1920 \\
0.3406 \\
0.3839 \\
-0.2880 \\
1.2047 \\
-1.4126 \\
-0.2215
\end{array}\right]
\end{equation*}

\hlok{The} bias of the output layer $b$ is a scalar:
\begin{equation*}
b = 0.1178
\end{equation*}

@@

\bibitem[Tian \em{et~al.}(2022)Tian, Chadha, and Aranas]{tian2022deformation}
Tian, Y.; Chadha, K.; Aranas, C.
\newblock Deformation-Induced Strengthening Mechanism in a Newly Designed L-40
 Tool Steel Manufactured by Laser Powder Bed Fusion.
\newblock {\em Acta Metall. Sin. (Engl. Lett.)} {\bf 2022}, \hlok{\emph{36}, 21--34}.
\newblock {\url{https://doi.org/10.1007/s40195-022-01461-z}}.%MDPI: Highlight without comment: newly added/revised information. Following are the same. Please confirm: OK

@@

\bibitem[Jia \em{et~al.}(2022)Jia, Chen, Rusinek, and Zhou]{jia2022thermo}
Jia, B.; Chen, P.; Rusinek, A.; Zhou, Q.
\newblock Thermo-viscoplastic behavior of DP800 steel at quasi-static,
 intermediate, high and ultra-high strain rates.
\newblock {\em Int. J. Mech. Sci.} {\bf 2022}, \hl{\emph{226}},
 107408.
\newblock {\url{https://doi.org/10.1016/j.ijmecsci.2022.107408}}.

@@

\bibitem[Rudnytskyj \em{et~al.}(2020)Rudnytskyj, Simon, Jech, and
 Gachot]{rudnytskyj2020constitutive}
\hlok{Rudnytskyj, A.; Simon, P.; Jech, M.; Gachot, C.} %MDPI: Refs 15 and 53 are the same. Please check and revise it. Ref 53, has been removed and cross references in the text changed.
\newblock Constitutive modelling of the 6061 aluminium alloy under hot rolling
 conditions and large strain ranges.
\newblock {\em Mater. Des.} {\bf 2020}, {\em 190},~108568.
\newblock {\url{https://doi.org/10.1016/j.matdes.2020.108568}}.

@@

\bibitem[Johnson and Cook(1983)]{Johnson-1983}
Johnson, G.R.; Cook, W.H.
\newblock {A constitutive model and data for materials subjected to large strains, high strain rates, and high temperatures}.
\newblock {In Proceedings of the 7th International Symposium on Ballistics, The
 Hague, The Netherlands, 19--21 April} {1983}; \hlok{pp. 541--547}.
%\newblock {\url{https://doi.org/10.1299/kikaia.65.1412}}. Wrong doi, doesn't exists

\bibitem[Chadha \em{et~al.}(2018)Chadha, Shahriari, and
 Jahazi]{chadha2018approach}
\hlok{Chadha, K.; Shahriari, D.; Jahazi, M.} %MDPI: Refs 18 and 51 are the same. Please check and revise it. Ok, Ref 51 has been removed and crossref has been updated in the text
\newblock An approach to develop Hansel--Spittel constitutive equation during
 ingot breakdown operation of low alloy steels. In {\em Frontiers in Materials
 Processing, Applications, Research and Technology}; Springer: \hlok{Berlin/Heidelberg, Germany,} %newly added information, please confirm: OK
 2018; pp.
 239--246.
\newblock {\url{https://doi.org/10.1007/978-981-10-4819-7_20}}.

@@

\bibitem[Jia \em{et~al.}(2021)Jia, Guan, Zang, Wang, and Lei]{Jia-2021}
\hlok{Jia, Z.; Guan, B.; Zang, Y.; Wang, Y.; Lei, M.} %MDPI: Refs 20 and 25 are the same. Please check and revise it: Ref 25 removed and crossref updated in text.
\newblock {Modified Johnson--Cook model of aluminum alloy 6016-T6 sheets at low
 dynamic strain rates}.
\newblock {\em Mater. Sci. Eng. A} {\bf 2021}, {\em
 820},~141565.
\newblock {\url{https://doi.org/10.1016/j.msea.2021.141565}}.

\bibitem[Liu \em{et~al.}(2021)Liu, Ma, and Fan]{liu2021modified}
Liu, X.; Ma, H.; Fan, F.
\newblock {Modified Johnson--Cook model of SWRH82B steel under different
 manufacturing and cold-drawing conditions}.
\newblock {\em J. Constr. Steel Res.} {\bf 2021}, {\em
 186},~106894.
\newblock \hlok{{\url{https://doi.org/10.1016/j.jcsr.2021.106894}}}. % Corrected doi

@@

\bibitem[Cheng and Mahnken(2021)]{Cheng-2021}
Cheng, C.; Mahnken, R.
\newblock {A modified Zerilli–Armstrong model as the asymmetric visco-plastic
 part of a multi-mechanism model for cutting simulations}.
\newblock {\em Arch. Appl. Mech.} {\bf 2021}, \hl{\emph{91}, 3869--3888}.
\newblock {\url{https://doi.org/10.1007/s00419-021-01982-6}}.

>>>>

%=================================================================
% MDPI internal commands - do not modify
% MDPI internal commands - do not modify
\firstpage{1}
\makeatletter
\setcounter{page}{\@firstpage}
\makeatother
\pubvolume{1}
\issuenum{1}
\articlenumber{0}
\pubyear{2023}
\copyrightyear{2023}
\externaleditor{Academic Editor: Ji Hoon Kim %MDPI: Please add it.
}
\datereceived{ 10 February 2023}
\daterevised{ 16 March 2023} % Comment out if no revised date
\dateaccepted{20 March 2023}
\datepublished{ }
%\datecorrected{} % For corrected papers: "Corrected: XXX" date in the original paper.
%\dateretracted{} % For corrected papers: "Retracted: XXX" date in the original paper.
\hreflink{https://doi.org/} % If needed use \linebreak
%\doinum{}
%\pdfoutput=1 % Uncommented for upload to arXiv.org

@@

\DeclareRobustCommand{\w}{\mbox{\large\ensuremath{\mathsf{w}}}}
\DeclareRobustCommand{\dotp}{\boldsymbol{\cdot}}
\DeclareRobustCommand{\e}[1]{{\rm e}^{#1}}
\DeclareRobustCommand{\lay}[1]{^{(#1)}}
\DeclareRobustCommand{\mdot}[1]{\accentset{\mbox{\bfseries .}}{#1}}
\DeclareRobustCommand{\ie}{i.e.,\@\xspace}
\DeclareRobustCommand{\eal}{et al.\@\xspace}
\DeclareRobustCommand{\eg}{e.g.,\@\xspace}
\DeclareRobustCommand{\RMSE}{\text{E}_\text{RMS}}
\DeclareRobustCommand{\MARE}{\text{E}_\text{MAR}}
\DeclareRobustCommand{\R}{\text{R}}
\DeclareRobustCommand{\ps}{\text{s}^{-1}}
\DeclareRobustCommand{\mr}[2]{\multirow{#1}{*}{#2}}
\DeclareRobustCommand{\MPa}{\text{MPa}}

@@

% Authors, for the paper (add full first names)
\Author{Pierre Tize Mha $^{1}$, Prashant Dhondapure $^{2}$, Mohammad Jahazi $^{2}$\orcidB{}, Amèvi Tongne $^{1}$\orcidC{} and Olivier Pantalé $^{1,}$*\orcidA{}}

@@

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{$^{1}$ \quad Laboratoire Génie de Production, INP/ENIT, Université de Toulouse, 47 Av d'Azereix, F-65016 Tarbes, France; ptizemha@enit.fr (P.T.M.); amevi.tongne@enit.fr (A.T.)\\
$^{2}$ \quad Department of Mechanical Engineering, École de Technologie Supérieure, 1100 Notre Dame St. W., Montréal, QC H3C 1K3, Canada; prashant-nagnath.dhondapure.1@ens.etsmtl.ca (P.D.); mohammad.jahazi@etsmtl.ca (M.J.)}

@@

% Keywords
\keyword{artificial neural network; constitutive flow law; analytical flow law; interpolation; extrapolation; Gleeble}

@@

\newcolumntype{L}{>{\raggedright\arraybackslash}X}
\newcolumntype{C}{>{\centering\arraybackslash}X}
\begin{tabularx}{\textwidth}{LCCCCCCC}
\toprule
\textbf{Element} & \textbf{C} & \textbf{Mn} & \textbf{Mo} & \textbf{Si} & \textbf{Ni} & \textbf{Cr} & \textbf{Cu} \\
\midrule
\textbf{Wt~\%} & $0.30$ & $0.89$ & $0.52$ & $0.34$ & $0.68$ & $1.86$ & $0.17$ \\
\bottomrule
\end{tabularx}
\label{tab:Composition}
\end{table}
Cylindrical samples were machined with an initial diameter of $d=10$~mm and a height of $h_0=15$~mm.
Hot compression tests were performed on a Gleeble-3800 thermomechanical simulator (see Figure \ref{fig:Gleeble3800}), for $5$ temperature levels, namely $1050~\celsius$, $1100~\celsius$, $1150~\celsius$, $1200~\celsius$, and $1250~\celsius$, with the $6$ strain rates of $0.001~\ps$, $0.01~\ps$, $0.1~\ps$, $1~\ps$, $2.0~\ps$, and $5~\ps$.
\begin{figure}[H]

@@

\includegraphics[width=0.99\columnwidth]{Figures/CompExp-JC-6}
\caption{Comparison between the experimental (dots) and predicted (lines) flow stresses $\sigma^y$ by the Johnson--Cook model.}
\label{fig:CompExp-JC-6}
\end{figure}
The JC model is unable to describe the evolution of the average flow stress for all strain and strain rate levels. The experimental flow stresses show a growth and then a decrease with strain, especially for low strain rates, while the JC model, by its formulation, only allows an increasing evolution of the flow stress $\sigma^y$ as a function of the strain independently of the strain rate value.
The discrepancy between the predicted and experimental values is large for low strains and sometimes acceptable for high strains.
As expected, the mathematical formulation of the Johnson--Cook flow law is unable to represent the stress drop at low strain rates, with the JC model increasing only monotonically with the strain.
Since most of the parameters are identified at low strain rates ($A$, $B$, and $n$), this results in a very poor fit of the model to the experimental data.

@@

\includegraphics[width=0.7\columnwidth]
{Figures/ANN-scheme-2HL}
\caption{Two hidden layers artificial neural network architecture with 3 inputs neurons (green) and 1 output neuron (red).}
\label{fig:ANN-2HL}
\end{figure}

Any hidden layer $k$, containing $n$ neurons, takes a weighted sum of the outputs $\overrightarrow{\hat{y}}$ of the immediately preceding layer $(k-1)$, containing $m$ neurons, given by the following~equation:
\begin{equation}
y_i\lay{k} = \sum_{j=1}^m w_{ij}\lay{k} \hat{y}_j^{(k-1)}+ b_i\lay{k},\label{eq:ANN1}
\end{equation}
where $y_i\lay{k}$ is the entry of the  $i$th neuron of layer $k$, $\hat{y}_j\lay{k-1}$ is the output of the $j$th neuron of layer $(k-1)$, $w_{ij}\lay{k}$ is the associated weight parameter between the  $i$th neuron of layer $k$ and the  $j$th neuron of layer $(k-1)$, and $b_i\lay{k}$ is the associated bias of the  $i$th neuron of layer $k$.
Those weights $w_{ij}$ and bias $b_i$, for each layer, are the training parameters of the ANN, which we have to adjust during the training procedure described in Pantalé \eal \cite{Pantale-2021, Pantale-2023}.
For the proposed model, we selected the Sigmoid activation function, so that each neuron in the hidden layer $k$ provides an output value ${\hat{y}}$ from the input value $y$ of the same neuron defined by Equation (\ref{eq:ANN1}) according to the following equation:
\begin{equation}
\hat{y}=\frac{1}{1 + \e{-y}}\label{eq:ANN2}
\end{equation}

@@

\textls[-25]{Once the training phase is over, the trained model can be used to predict the behavior of the medium carbon alloy as a function of the input data, similarly to what was done with the analytical models.
One can either use the model directly by providing it with new input data or retrieve the $180$ parameters identified during the training and inject them into a mathematical model based on Equations (\ref{eq:ANN1}) and (\ref{eq:ANN2}), which can be implemented in any language (\eg in FORTRAN for use on the Abaqus Explicit FEA code), as proposed in Pantalé \eal \cite{Pantale-2021, Pantale-2023}.
For compactness, the parameters of the ANN model and the complete procedure to compute the flow stress $\sigma^y$ from the input data are provided in Appendix \ref{sec:Appendix}.}

@@

The ANN, Arrhenius and PTM models are the only models that take into account softening with the deformation of medium carbon at a low strain rate, unlike the other three models, which only present an increase in the flow stress with the strain, irrespective of the strain rate and temperature, hence their poor performance in predicting the behavior of this material and, more particularly, at low strain rates.
The parameters reported in \mbox{Table \ref{tab:Errors}} and the correlations that can be seen in Figures \ref{fig:CompExp-JC-6}--\ref{fig:CompExp-PTM-6} and \ref{fig:CompExp-3-15-7-1-sigmoid} allow concluding that the ANN model is the most efficient of all the models presented when it comes to describing the behavior of the medium carbon alloy for high-temperature deformation applications.

@@

\includegraphics[width=0.98\columnwidth]
{Figures/CompExt}
\caption{Comparison between the experimental (dots) and predicted (lines) flow stresses $\sigma^y$ for $\mdot\varepsilon=5~\ps$.}
\label{fig:CompExt}
\end{figure}
Table \ref{tab:ExtVal} shows the $\MARE$ and $\RMSE$ deviations between the different models and the experimental data calculated either for the $5$ identified strain rates (lines referred as id. $\mdot\varepsilon$), the $6$ strain rates (lines referred as all $\mdot\varepsilon$), or only on the strain rate $\mdot\varepsilon=5~\ps$.
\begin{table}[H]

@@

\acknowledgments{The authors acknowledge Jean-Benoit Morin, Director of Metallurgy and Quality from Finkl Steel-Sorel, Abdelhalim Loucif from the R\&D department of Finkl Steel-Sorel, Ecole de Technologie Superieure, and Ecole Nationale d'Ingenieurs de Tarbes, France, for providing technical data, materials, and testing facilities.}%MDPI: We removed titles here: OK

@@

The biases of the first hidden layer $\overrightarrow{b_1}$ is a $15$-component vector:
\begin{equation*}
\overrightarrow{b}_1 = \left[
\begin{array}{r}
5.9164 \\
-1.9074 \\
-2.6837 \\
-1.0954 \\
-0.9509 \\
3.1682 \\
-4.3964 \\
0.6343 \\
-5.0676 \\
2.0228 \\
1.1267 \\
-0.9671 \\
-0.6263 \\
2.3110 \\
-0.3037
\end{array}\right]
\end{equation*}

The weight matrix for the second hidden layer $\w_2$ is a $7\times15$ matrix:
\begin{equation*}
\w_2^T = \left[
\begin{array}{rrrrrrr}
-0.5783 & 1.2724 & 0.5747 & 0.6449 & -4.2203 & -0.2380 & 0.2591 \\
-0.4852 & 5.2807 & 0.8888 & -8.2324 & -2.0075 & -0.6474 & -1.0787 \\
4.4499 & -0.0137 & 0.1657 & 0.3198 & 4.9765 & -1.2503 & 0.8219 \\
1.7571 & 0.7730 & 0.0208 & -1.3316 & -0.8945 & -0.7284 & -0.1831 \\
-1.0866 & 0.1330 & -0.8615 & -0.1283 & 0.2218 & -0.1772 & -2.7458 \\
-0.3925 & 1.3994 & 0.0630 & -1.8397 & -1.1047 & -1.9839 & 0.5767 \\
-0.2121 & 0.9977 & 1.2028 & -9.6525 & 0.5520 & 0.1062 & -0.0409 \\
-1.1518 & -1.6402 & -4.1501 & -1.0759 & 0.4749 & -2.8350 & 0.9225 \\
-1.1453 & -0.2173 & -0.1382 & 0.8264 & -0.5125 & 0.1882 & -0.8654 \\
-4.3301 & -0.3711 & -7.4305 & 3.5926 & -9.6217 & -1.2375 & 1.6171 \\
2.3907 & -1.0085 & -0.8828 & -1.1891 & 0.9947 & 1.1178 & -1.0953 \\
-1.5955 & 1.6313 & 0.4916 & 0.1906 & -1.9216 & -1.4140 & 1.3827 \\
-1.6985 & 1.4277 & -3.4462 & -8.3777 & -1.2132 & -1.2158 & 2.8512 \\
-1.9954 & -2.0159 & -8.3455 & -0.5205 & 0.2942 & -1.3337 & 0.2026 \\
4.3040 & -0.7164 & -1.0859 & 3.4294 & -23.8003 & 12.5859 & 7.3721
\end{array}\right]
\end{equation*}

The biases of the second hidden layer $\overrightarrow{b_2}$ is a seven-component vector:
\begin{equation*}
\overrightarrow{b}_2 = \left[
\begin{array}{r}
0.7534 \\
0.9473 \\
0.6055 \\
-0.7793 \\
-1.0305 \\
-1.5779 \\
-0.1471
\end{array}\right]
\end{equation*}

The weight vector for the output layer $\overrightarrow{w}$ is a seven-component vector:
\begin{equation*}
\overrightarrow{w} = \left[
\begin{array}{r}
0.1920 \\
0.3406 \\
0.3839 \\
-0.2880 \\
1.2047 \\
-1.4126 \\
-0.2215
\end{array}\right]
\end{equation*}

The bias of the output layer $b$ is a scalar:
\begin{equation*}
b = 0.1178
\end{equation*}

@@

\bibitem[Tian \em{et~al.}(2022)Tian, Chadha, and Aranas]{tian2022deformation}
Tian, Y.; Chadha, K.; Aranas, C.
\newblock Deformation-Induced Strengthening Mechanism in a Newly Designed L-40
 Tool Steel Manufactured by Laser Powder Bed Fusion.
\newblock {\em Acta Metall. Sin. (Engl. Lett.)} {\bf 2022}, \emph{36}, 21--34.
\newblock {\url{https://doi.org/10.1007/s40195-022-01461-z}}.%MDPI: Highlight without comment: newly added/revised information. Following are the same. Please confirm: OK

@@

\bibitem[Jia \em{et~al.}(2022)Jia, Chen, Rusinek, and Zhou]{jia2022thermo}
Jia, B.; Chen, P.; Rusinek, A.; Zhou, Q.
\newblock Thermo-viscoplastic behavior of DP800 steel at quasi-static,
 intermediate, high and ultra-high strain rates.
\newblock {\em Int. J. Mech. Sci.} {\bf 2022}, \emph{226},
 107408.
\newblock {\url{https://doi.org/10.1016/j.ijmecsci.2022.107408}}.

@@

\bibitem[Rudnytskyj \em{et~al.}(2020)Rudnytskyj, Simon, Jech, and
 Gachot]{rudnytskyj2020constitutive}
Rudnytskyj, A.; Simon, P.; Jech, M.; Gachot, C. %MDPI: Refs 15 and 53 are the same. Please check and revise it. Ref 53, has been removed and cross references in the text changed.
\newblock Constitutive modelling of the 6061 aluminium alloy under hot rolling
 conditions and large strain ranges.
\newblock {\em Mater. Des.} {\bf 2020}, {\em 190},~108568.
\newblock {\url{https://doi.org/10.1016/j.matdes.2020.108568}}.

@@

\bibitem[Johnson and Cook(1983)]{Johnson-1983}
Johnson, G.R.; Cook, W.H.
\newblock {A constitutive model and data for materials subjected to large strains, high strain rates, and high temperatures}.
\newblock {In Proceedings of the 7th International Symposium on Ballistics, The
 Hague, The Netherlands, 19--21 April} {1983}; pp. 541--547.
%\newblock {\url{https://doi.org/10.1299/kikaia.65.1412}}. Wrong doi, doesn't exists

\bibitem[Chadha \em{et~al.}(2018)Chadha, Shahriari, and
 Jahazi]{chadha2018approach}
Chadha, K.; Shahriari, D.; Jahazi, M. %MDPI: Refs 18 and 51 are the same. Please check and revise it. Ok, Ref 51 has been removed and crossref has been updated in the text
\newblock An approach to develop Hansel--Spittel constitutive equation during
 ingot breakdown operation of low alloy steels. In {\em Frontiers in Materials
 Processing, Applications, Research and Technology}; Springer: Berlin/Heidelberg, Germany, %newly added information, please confirm: OK
 2018; pp.
 239--246.
\newblock {\url{https://doi.org/10.1007/978-981-10-4819-7_20}}.

@@

\bibitem[Jia \em{et~al.}(2021)Jia, Guan, Zang, Wang, and Lei]{Jia-2021}
Jia, Z.; Guan, B.; Zang, Y.; Wang, Y.; Lei, M. %MDPI: Refs 20 and 25 are the same. Please check and revise it: Ref 25 removed and crossref updated in text.
\newblock {Modified Johnson--Cook model of aluminum alloy 6016-T6 sheets at low
 dynamic strain rates}.
\newblock {\em Mater. Sci. Eng. A} {\bf 2021}, {\em
 820},~141565.
\newblock {\url{https://doi.org/10.1016/j.msea.2021.141565}}.

\bibitem[Liu \em{et~al.}(2021)Liu, Ma, and Fan]{liu2021modified}
Liu, X.; Ma, H.; Fan, F.
\newblock {Modified Johnson--Cook model of SWRH82B steel under different
 manufacturing and cold-drawing conditions}.
\newblock {\em J. Constr. Steel Res.} {\bf 2021}, {\em
 186},~106894.
\newblock {\url{https://doi.org/10.1016/j.jcsr.2021.106894}}. % Corrected doi

@@

\bibitem[Cheng and Mahnken(2021)]{Cheng-2021}
Cheng, C.; Mahnken, R.
\newblock {A modified Zerilli–Armstrong model as the asymmetric visco-plastic
 part of a multi-mechanism model for cutting simulations}.
\newblock {\em Arch. Appl. Mech.} {\bf 2021}, \emph{91}, 3869--3888.
\newblock {\url{https://doi.org/10.1007/s00419-021-01982-6}}.
